---
title: "HW 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
source("analysis.R")
```

One of the most pressing issues in America today is the disproportionate 
rates of incarceration of POC. To better understand this issue, I am going to 
analyze the ratio of average incarceration rates by US regions of black 
populations to white populations. This will show just *how much* more likely a
POC are to be incarcerated than white people are.



# Values

```{r echo = F}
avg_btw_ratios
highest_btw_ratio_2016
highest_btw_ratio_2006
county_with_highest_btw_ratio
change_in_btw_ratio_10_yrs
```


# Chart 1

This chart shows how these rates are changing over time.

```{r echo = F}
rate_over_time
```


# Chart 2

This chart shows how as the incarceration rate of white people increases in
communities, the incarceration rate of black people increases by even more.

```{r echo = F}
b_vs_w_pop_rate
```


# Map

This map shows the rates by county in Washington State.


```{r echo = F}
black_incarceration_rate_map
```
