---
title: "HW 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
source("analysis.R")
```


# Intro

One of the most pressing issues in America today is the disproportionate 
rates of incarceration of POC. To better understand this issue, I am going to 
analyze the ratio of average incarceration rates by US regions of black 
populations to white populations. This will show just *how much* more likely a
POC are to be incarcerated than white people are.


# Values

This section will present some values/patterns that arose during this 
investigation. The average ratio of incarceration rate of black Americans to
that of white Americans per year is shown in the table below:
`r kable(avg_btw_ratios)` The highest ratio in a single county in 2006 is
`r highest_btw_ratio_2006`. This can be compared the highest ratio in 2016 which
was `r highest_btw_ratio_2016`. The County and State which held this ratio was
`r county_with_highest_btw_ratio`. The change in average the ratio over most 
recent 10 years across all counties is `r change_in_btw_ratio_10_yrs`.


# Trend Over Time

```{r echo = F}
rate_over_time
```

This chart shows how the average incarceration rates of various 5 races
in America have changed from 1990 to 2016.
While the rate for each race seems to be trending upward, it can be seen
the rate of black Americans is significantly higher than that of any other race.
It should also be noted that the rate for white Americans is one of the lowest.


# Comparing Statistics

```{r echo = F}
b_vs_w_pop_rate
```

This purpose of this chart is to visualize how as the incarceration rate of
white Americans increases in communities, the incarceration rate of black
Americans increases by even more. The **1:1 ratio** line is included as a
point of reference of how far off these values are from being an even.


# Mapping The Issue in Washington State

```{r echo = F}
black_incarceration_rate_map
```

This map shows the incarceration rate of the black population by county
in Washington State. The purpose of this is to show where the problem is the
most prevalent in our home state.
